comgen-outline

### 2017-07-04 paper/comgen-paper.Rmd
add support for saved habituals model results

	var stableFrequency = {
		male: {
			mu: uniformDrift({a: -5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:5, width: 1})
		},
		female: {
			mu: uniformDrift({a:-5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:5, width: 1})
		}
	}

@@

```{r habituals-fullmodel}
n_chains <- 1
n_samples <- 10000
burn <- n_samples
lg <- 5
i <- 1
model_prefix <- "results-habituals-jointModel-S1-"

m.hab.samp <- data.frame()
for (i in seq(1, n_chains)){
  mi <- fread(paste(project.path,  "models/habituals/results/", 
                    model_prefix, "smtncs_habitual-",
                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  m.samp.i <- mi %>% mutate(chain = i)
  m.hab.samp <- bind_rows(m.hab.samp, m.samp.i)
}

n_chains <- 1
n_samples <- 1000
burn <- n_samples
lg <- 5
i <- 1
m.hab.fixed.samp <- data.frame()
for (i in seq(1, n_chains)){
  mi <- fread(paste(project.path,  "models/habituals/results/", 
                    model_prefix, "smtncs_some-",
                    n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  m.samp.i <- mi %>% mutate(chain = i)
  m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, m.samp.i)
}

@@

@@

@@

#### Methods

We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
None of the participants had completed Expt. 3a.
The only difference from Expt. 3a is the dependent measure. 
On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2).
The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.

#### Results

>>>>

	var stableFrequency = {
		male: {
			mu: uniformDrift({a: -5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:10, width: 1})
		},
		female: {
			mu: uniformDrift({a:-5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:10, width: 1})
		}
	}

@@

```{r habituals-fullmodel}
n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20
model_prefix <- "results-habituals-jointModel-S1-"

# m.hab.samp <- data.frame()
# m.hab.fixed.samp <- data.frame()

# for (i in seq(1, n_chains)){
#   mi <- fread(paste(project.path,  "models/habituals/results/",
#                     model_prefix, "smtncs_habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))
# 
#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
#                     model_prefix, "smtncs_some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
# 
# }
# 
# save(m.hab.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.hab.fixed.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

Another shortcoming of this fixed threshold is illuminated by our manipulation of target frequency.
With a fixed threshold on what makes a statement true or false, any two points that lie above the threshold are indistinguishable. 
Thus, this model makes the same predictions for different target frequencies in the same event.
For example, the model endorses somebody who hikes three times every two years the same as somebody who hikes three times every month.

@@

```{r habituals-predictive-rsa}

@@

We recruited `r n.subj.hab.pred.endorse` participants from MTurk, using the same criterion as Expt. 2b.
The experiment took `r round(ave.seconds.hab.pred.endorse / 60)` minutes on average on participants were compensated \$0.40 for their work.
None of the participants had completed Expt. 2c.
The only difference from Expt. 2c is the dependent measure. 
On each trial, participants were asked if they agreed or disagreed with the corresponding habitual sentence (as in Expt. 2b).
The experiment can be viewed at \url{http://stanford.edu/~mtessler/habituals/experiments/truth-judgments/tj-3-preventative.html}.
